\section{\uppercase{Introduction}}
\label{sec:introduction}

This section introduces Simulation-based Digital Twins and the optimization process in simulation-based Digital Twins. 
\begin{itemize}
    \item Further, we discuss Simulation-based optimization (SBO) (adheres to proposed work) and Back-box optimization. 
\end{itemize}

\subsection{Literature review}
relevant literature on Metamodels/Surrogate Models.
\begin{itemize}
    \item A brief survey of Simulation-Based Optimization using Surrogate Models and the most popular Surrogate Models/Metamodels being used to increase the efficiency of the optimization process in SBO.
    \item Different Metamodels are available (Linear Regression, Response surface, Decision Tree, Radial Basis Functions, Kriging, Neural Networks).
\end{itemize}

\subsection{Motivation for the Case Study}
Choosing the appropriate Metamodel and optimizer is crucial for a reasonably accurate and fast optimization process.
The Simulation Model component in Digital Twin:
\begin{itemize}
    \item is often complex and time-consuming
    \item is Stochastic
    \item the number of input parameters is large
\end{itemize}
The optimization process needs quick evaluations of the simulation model for different input parameter settings. Metamodel facilitate it.
\subsection{Metamodels}
\begin{itemize}
    \item Definition
    \item Types of Metamodels: 
    \begin{itemize}
        \item Gaussian Process Regression,
        \item Neural Networks Metamodels.
    \end{itemize}
    \item Challenges in choosing a Metamodel.
    \item Metamodel parameters
\end{itemize}

\subsection{Open Source Optimizers}
\begin{itemize}
    \item List of \textit{scipy.optimize} optimizers and brief introduction.
    \item Challenges in choosing a suitable optimizer.
\end{itemize}
The organization of the paper.
\section{\uppercase{The Case study: Inventory optimization in Supply Chain}}
\subsection{Problem Setting}
\begin{itemize}
    \item Description of the system
    \item Assumptions, Input parameters, Performance measures, Bounds
\end{itemize}

\subsection{The Simulation Model}
\begin{itemize}
    \item Estimating parameter values (num of days, num of simulations)
    \item Analysis of time and space complexity
    \item Exhaustive evaluation 
    \item Visualization (contours/heatmaps/3D sections)
\end{itemize}
\subsection{Fitting a Metamodel}

\begin{itemize}
    \item Estimation of parameter values for Metamodels\\
    \textbf{GPR:}
    \begin{enumerate}
        \item Which Kernel to use?
        \item Kernel parameter values.
    \end{enumerate}
     \textbf{NN:} 
     \begin{enumerate}
         \item Type of NN,
         \item Number of hidden layers,
         \item number of neurons in each layer
     \end{enumerate}
    \item Sampling Method?
    \item Estimating $N$ (number of points to sample)
    \item validating the Metamodel (measure of match between $f(X)$ and $g(X))$
    \begin{enumerate}
        \item accuracy of $g(X)$ (sum square difference)
        \item does it capture original maxima/minima?
        \item does it retain gradient information of $f(X)$?
    \end{enumerate}
    \item Visualization (contours/heat-maps/3D sections)
\end{itemize}

\subsection{Optimization}
\begin{itemize}
    \item Optimizing the system \\(without Metmodels: Exhaustive Evaluation)\\ Estimating the \textit{actual minimum} 
    \item optimization with Metamodels
\end{itemize}
\section{\uppercase{Results}}
\begin{itemize}
    \item Comparative results of optimization process with and without Metamodels. (table)
    \item Analysis of time complexity
    \item Listing/concluding of Metamodel and optimizer pairs that performed best
\end{itemize}
\section{\uppercase{Conclusion}}
\begin{itemize}
    \item Conclusion
    \item Future Work
\end{itemize}